### 2015-07-11 cover-collab.tex
made addtions to the collaborative cover page

\vfill
\begin{center}
\textbf{\huge Cover Page Supplement for Collaborations}
\end{center}

\vfill

@@

\input{cover-collab-table}

\vfill
\begin{center}
\textbf{\large Leadership Structure}
\medskip
\end{center}

This is a collaborative proposal between 
Oak Ridge National Laboratory, and
Sandia National Laboratories, and
Rutgers University, and
University of California, Santa-Cruz.

@@

\vfill
\begin{center}
\textbf{\large Facilities, Equipment, and Resources}
\medskip
\end{center}

This proposal brings together the expertiese and facilities from two
national laboratories, Oak Ridge National Laboratory and Sandia National
Laboratories, and two universities, Rutgers University and University of
California, Santa-Cruz. 
 In addition, by
sharing experiese and personnel costs, it represents
a collaboration with other large programs within the Office of
Science, including on data management and exascale monitoring, as well as
ongoing development of the Sirocco file-system. 
The proposed work will leverage existing facilities at all three
sites, including leadership machines at ORNL and SNL, and also utilize
storage oriented cluster systems at all locations. The PIs will also combine
their experience with production middleware and storage system software
development and their collaboration with leading application scientists to
better guide the assumptions underlying this effort.

%% Include a description of each collaborating institution’s facilities,
%% equipment, and resources that will be made available to the
%% collaborative group.

\vfill
\begin{center}
\textbf{\large Summary Budget Information}
\medskip
\begin{tabular}{| l | l | l | r | r | r | r |} \hline
Role & Name & Institution & Year 1 (\$K) & Year 2 (\$K) &   Year 3 (\$K) & Total (\$K) \\
\hline
Lead-PI & Scott Klasky & ORNL & {\$}570 &  {\$}570 &  {\$}570 &   {\$}1,710\\
Co-PI & Jay Lofstead & Sandia  &  {\$}350 &  {\$}350 &  {\$}350 &  {\$}1,050 \\
Co-PI & Carlos  Maltzahn & UCSC  &  {\$}160 &  {\$}160 &  {\$}160 &  {\$}480 \\
Co-PI & Manish Parashar & Rutgers &  {\$}170 &  {\$}170 &  {\$}170 &  {\$}510  \\
\hline
{\bf Totals}  & & & {\bf  {\$}1,250} & {\bf  {\$}1,250} & {\bf  {\$}1,250} & {\bf  {\$}3,750}\\
\hline
\end{tabular}
\end{center}

>>>>

\newpage

\begin{center}
\textbf{\huge Cover Page Supplement for Collaborations}
\end{center}

@@

%\input{cover-collab-table}
\begin{center}
\textbf{\large Leadership Structure}
\end{center}

This is a collaborative proposal between 
Oak Ridge National Laboratory, and
Sandia National Laboratories, and
Rutgers University, and
University of California, Santa-Cruz. 
PI Klasky will be responsible for project oversight, reporting to DOE, and
final decision making in event of major disagreements.
We define an area lead for each major research area plus
an integration lead responsible for coordinating periodic integration tests. The area leads plus the project PIs
form the management team, which will meet weekly to review progress and revise plans as needed.

@@

\begin{center}
\textbf{\large Facilities, Equipment, and Resources}
\end{center}
This proposal brings together the expertise and facilities from two
national laboratories, Oak Ridge National Laboratory and Sandia National
Laboratories, and two universities, Rutgers University and University of
California, Santa-Cruz. 
 In addition, by
sharing expertise and personnel costs, it represents
a collaboration with other large programs within the Office of
Science, including on data management and exascale monitoring, as well as
ongoing development of the Sirocco file-system. 
The proposed work will leverage existing facilities at all three
sites, including leadership machines at ORNL and SNL, and also utilize
storage oriented cluster systems at all locations. The PIs will also combine
their experience with production middleware and storage system software
development and their collaboration with leading application scientists to
better guide the assumptions underlying this effort.

%% Include a description of each collaborating institution’s facilities,
%% equipment, and resources that will be made available to the
%% collaborative group.
\vspace{2ex}

\noindent
{\bf Description of facilities, equipment, and resources}: We summarize these here; detailed information is provided in the supplementary documents.
\begin{itemize}
\item
{\bf Oak Ridge National Laboratory}. \underline{Computers}:
Oak Ridge Leadership Facility (discretionary time for SNS experiments), including
Titan, Gaea (a Cray XE6 system), the ORNL Institutional Cluster (OIC),
and Frost. A cloud resource, CADES, can be made available to
researchers in this project, as well as the sith cluster which has a Lustre file
sysem, 2 SSD on each node, and access to the cneter wide Spider file system.
 \underline{Networks}: 100 Gbps connection to ESnet.
\vspace{-1ex}
\item
{\bf Rutgers University}. \underline{Computers}: Excalibur BGP, Clusters, CometCloud, and CAPER testbeds. \underline{Networks}: 10 Gbps to Internet2.
\vspace{-1ex}
\item
{\bf Sandia National Laboratory}.
\underline{Computers}: 264 TF Red Sky system and many testbed systems
\underline{Networks}: 100 Gbps to ESnet
\item
{\bf UCSC}.
\underline{Computers}:  48 node system and access to the ISSDM storage resource
\underline{Networks}: 1 Gbps to ESnet

\end{itemize}

\begin{center}
\textbf{\large Summary Budget Information}
\medskip
\begin{tabular}{| l | l | l | r | r | r | r |} \hline
Role & Name & Institution & Year 1 (\$K) & Year 2 (\$K) &   Year 3 (\$K) & Total (\$K) \\
\hline
Lead-PI & Scott Klasky & ORNL & {\$}570 &  {\$}570 &  {\$}570 &   {\$}1,710\\
Co-PI & Jay Lofstead & Sandia  &  {\$}350 &  {\$}350 &  {\$}350 &  {\$}1,050 \\
Co-PI & Carlos  Maltzahn & UCSC  &  {\$}160 &  {\$}160 &  {\$}160 &  {\$}480 \\
Co-PI & Manish Parashar & Rutgers &  {\$}170 &  {\$}170 &  {\$}170 &  {\$}510  \\
\hline
{\bf Totals}  & & & {\bf  {\$}1,250} & {\bf  {\$}1,250} & {\bf  {\$}1,250} & {\bf  {\$}3,750}\\
\hline
\end{tabular}
\end{center}
